Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2017-01-04 ms.tex
I replaced the PDF files of the time series wiht PNGs since the file sizes were way too big.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
	\label{fig:tserPfold}
\end{figure*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$) which is a better match to the data.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.png}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.png}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
	\label{fig:tserPfold}
\end{figure*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$ =7.9) which is a better match to the data.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}
